Potential of I/O-Aware Workflows in Climate and Weather

### 2020-05-02 paper.tex
Minor fixes

  \item \textbf{Job} provides the environment with the resources and it runs the user-provided program or script on one of the nodes allocated for it.
  Local variables containing information about the environment of the batch job, e.g., the compute nodes allocated, and then enacts the Cylc provided script on one node.

@@

Related work can be categorised into:
1) Technology that exploits heterogeneous storage environments and supports user-directed policies and
2) Solutions for workflow processing.

@@

The storage community had also adjusted various higher-level software to support storage tiering on top of several storage systems. For instance, ADIOS provides in-memory staging that had been exploited by a variety of applications~\cite{slawinska2013maya}.
Hermes~\cite{kougkas2020acceleration} provides a multi-tiered I/O buffering system with pre-fetcher that provides several data placement policies.
iRODS~\cite{rajasekar2010irods} is a rule-oriented data system that allows scientists to organise data into shareable collections and provides several patterns for workflows considering data locality and data migration/replication.
% and provide metadata such as the data life cycle.
Finally, there have also been extensions to batch schedulers to perform data staging for utilising node-local storage, for example, NORNS~\cite{miranda2019norns} as an extension to Slurm.

\smallskip

@@

\begin{lstlisting}[caption = Example of an ESDM configuration file (\texttt{esdm.conf}), label=lst:esdm.conf]
"backends": [
    {"type": "POSIX", "id": "work1", "target": "/work/lustre01/projectX/",
        "performance-model" : {"latency" : 0.00001, "throughput" : 500000.0},
        "max-threads-per-node" : 8,
        "max-fragment-size" : 104857600,
        "max-global-threads" : 200,
        "accessibility" : "global"
    },
    {"type": "POSIX", "id": "work2", "target": "/work/lustre02/projectX/",
        "performance-model" : {"latency" : 0.00001, "throughput" : 200000.0},
        "max-threads-per-node" : 8,
        "max-fragment-size" : 104857600,
        "max-global-threads" : 200,
        "accessibility" : "global"
    },
    {"type": "POSIX", "id": "tmp", "target": "/tmp/esdm/",
        "performance-model" : {"latency" : 0.00001, "throughput" : 200.0},
        "max-threads-per-node" : 0,
        "max-fragment-size" : 10485760,
        "max-global-threads" : 0,
        "accessibility" : "local"
    }
],
"metadata": {"type": "POSIX",
        "id": "md",
        "target": "./metadata",
        "accessibility" : "global"
    }
\end{lstlisting}

@@

\begin{lstlisting}[caption = External Cylc I/O-workflow configuration file (\texttt{io.cylc}), label=lst:cylc]
[Task 1]
  [[inputs]]
    topography = "/pool/input/app/config/topography.dat"
    checkpoint = "[Task 1].checkpoint$(CYCLE - 1)"
    init       = "/pool/input/app/config/init.dat"

@@

@@

  \item \textbf{\color{red}{EIOS}} The ESDM I/O Scheduler reads the information about the workflow (\texttt{flow.cylc} and \texttt{io.cylc} configuration files) and acts depending on the stage of the execution.
  EIOS consists of several subcomponents:
    \begin{itemize}

@@

\section{Conclusions}
\label{sec:conclusions}

>>>>

  \item \textbf{Job} provides the environment with the resources and it runs the user-provided program or script on one of the nodes allocated for it.
  Local variables containing information about the environment of the batch job, e.g., the compute nodes allocated, enacts the Cylc provided script on the node.

@@

Related work can be categorised into:
1) Technology that exploits heterogeneous storage environments and supports user-directed policies and
2) Solutions for workflow processing.\\

@@

The storage community had also adjusted various higher-level software to support storage tiering on top of several storage systems. For instance, ADIOS provides in-memory staging that had been exploited by a variety of applications~\cite{slawinska2013maya}.
Hermes~\cite{kougkas2020acceleration} provides a multi-tiered I/O buffering system with pre-fetcher that provides several data placement policies.
iRODS~\cite{rajasekar2010irods} is a rule-oriented data system that allows scientists to organise data into shareable collections and provides several patterns for workflows considering data locality and data migration/replication.
% and provide metadata such as the data life cycle.
Finally, there have also been extensions to batch schedulers to perform data staging for utilising node-local storage, for example, NORNS~\cite{miranda2019norns} as an extension to Slurm.\\

%\smallskip

@@

\begin{figure}[!ht]

\begin{lstlisting}
"backends": [
    {"type": "POSIX", "id": "work1", "target": "/work/lustre01/projectX/",
        "performance-model" : {"latency" : 0.00001, "throughput" : 500000.0},
        "max-threads-per-node" : 8,
        "max-fragment-size" : 104857600,
        "max-global-threads" : 200,
        "accessibility" : "global"
    },
    {"type": "POSIX", "id": "work2", "target": "/work/lustre02/projectX/",
        "performance-model" : {"latency" : 0.00001, "throughput" : 200000.0},
        "max-threads-per-node" : 8,
        "max-fragment-size" : 104857600,
        "max-global-threads" : 200,
        "accessibility" : "global"
    },
    {"type": "POSIX", "id": "tmp", "target": "/tmp/esdm/",
        "performance-model" : {"latency" : 0.00001, "throughput" : 200.0},
        "max-threads-per-node" : 0,
        "max-fragment-size" : 10485760,
        "max-global-threads" : 0,
        "accessibility" : "local"
    }
],
"metadata": {"type": "POSIX",
        "id": "md",
        "target": "./metadata",
        "accessibility" : "global"
    }
\end{lstlisting}

\caption{Example of an ESDM configuration file (\texttt{esdm.conf})}
\label{lst:esdm.conf}
\end{figure}

@@

\begin{figure}[!ht]

\begin{lstlisting}
[Task 1]
  [[inputs]]
    topography = "/pool/input/app/config/topography.dat"
    checkpoint = "[Task 1].checkpoint$(CYCLE - 1)"
    init       = "/pool/input/app/config/init.dat"

@@

\caption{External Cylc I/O-workflow configuration file (\texttt{io.cylc})}
\label{lst:cylc}
\end{figure}

@@

  \item \textbf{EIOS} The ESDM I/O Scheduler reads the information about the workflow (\texttt{flow.cylc} and \texttt{io.cylc} configuration files) and acts depending on the stage of the execution.
  EIOS consists of several subcomponents:
    \begin{itemize}

@@

\section*{Conclusions}
\label{sec:conclusions}
